\Large \bf Relationship of Weather and Maize Yields in Kenya

### 2018-11-16 writing/draft1/draftMonika10.tex
writing

\begin{enumerate}
\item Basic model which only includes seasonal precipitation and average seasonal temperature
\item The preferred specification which includes the significant weather aggregates (see the preliminary results in Table \ref{KenARe11})

@@

\end{enumerate}
\item Verbal description and interpretation of the results in table
\item Discussion and Conclusion:

	\end{itemize}
\section{Conclusion}\label{Conclusion}

@@

	\begin{itemize}
	\item[$\boldsymbol{\rightarrow}$] We can stress the importance of focusing the forecast on the climate characteristics (or measures) which we find significant in our models
\end{itemize}

>>>>

\begin{enumerate}
\item Base model which only includes seasonal precipitation and average seasonal temperature
\item The preferred specification which includes the significant weather aggregates (see the preliminary results in Table \ref{KenARe11})

@@

\end{enumerate}
\item Verbal description and interpretation of the results
\item Estimates of future impacts

\begin{itemize}
\item Comparison of estimates accuracy of the predictions from the base model and the preferred specification

		\begin{itemize}
		\item choose two points in time (past). Imagine we are in the earlier of the two time points and we want to make a prediction of yields in the future point. Compare the predictions of the base model and the predictions of the preferred specification. Here, we assume that we know the forecast of the weather measures- variables which are used in the models. We can use the real weather data instead of the forecast. This will demonstrate why is it important to not only forecast totals/means but also other characteristics (measures) of weather/climate
		\item Graphical comparison, possibly using barplots

		\end{itemize}

\end{itemize}

	\end{itemize}
\section{\textcolor{black}{Conclusion}}\label{Conclusion}

@@

	\begin{itemize}
	\item[$\boldsymbol{\rightarrow}$] \textbf{We can stress the importance of focusing the forecast on the climate characteristics (or measures) which we find significant in our models}
\end{itemize}
